Spike Spectra for Recurrences

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
start commenting the requests

% Authors, for the paper (add full first names)
\Author{\hl{K. Hauke Kraemer} %MDPI: Please carefully check the accuracy of names and affiliations.
 $^{1,}$*\orcidA{}, Frank Hellmann $^{1}$, Mehrnaz Anvari $^{1}$\orcidB{}, \hl{J\"urgen Kurths} %MDPI: The name of this author is different from the submitting system. Please confirm which one is correct.
 $^{1,2,\highlighting{3} %MDPI: 
}$ and Norbert Marwan $^{1,2,\highlighting{4} %MDPI: 
,}$*\orcidC{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, Germany; \hl{hellmann@pik-potsdam.de (F.H.); anvari@pik-potsdam.de (M.A.); kurths@pik-potsdam.de (J.K.)} %MDPI: We added the email addresses here according to the submitting system. Please confirm.
\\
$^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
\hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes.
 \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany\\
\hl{$^{4}$} \quad Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany}

@@

Recurrence plots (RPs) provide a vivid representation of complex dynamics $\vec{x}_i$ stemming from potentially high dimensional systems \cite{marwan2007}
\begin{equation}\label{eq_rp_definition}
R_{i,j}(\varepsilon) = \Theta\left(\varepsilon - D_{i,j}\right) 
= \Theta\left(\varepsilon - \| \vec{x}_i - \vec{x}_j\|\right), \qquad \vec{x} \in \mathbb{R}^d, \quad i,j \in [1,\ldots, N],
\end{equation}
where $\mathbf{R}$ \hl{is} %MDPI: There is no bold in other places in the text, please confirm whether the bold here needs to be retained
 the recurrence matrix, $\vec{x}_i$ is the state vector at time 
$t = \Delta t \cdot i$ ($\Delta t$ the sampling time), $N$ is the number of
sampling points (or length of data series), and $d$ is the dimension of the system.
The crucial free parameter $\varepsilon$ is the recurrence threshold, determining what is a recurrence
and, thus, the visible structures in the RP. It can be chosen such that the recurrence rate 
$RR(\varepsilon)=N^{-2}\sum_{i,j}^N R_{i,j}(\varepsilon)$ exhibits a certain value \cite{kraemer2018}.
The simple idea to track recurring states of the $d$-dimensional trajectory $\vec{x}_i$ of the system under study not only allows for a beneficial visualization of the dynamics, 
but also for its 
quantification, using certain structures in the RP, such as diagonal or vertical lines \cite{marwan2007}.

>>>>

% Authors, for the paper (add full first names)
\Author{\hl{K. Hauke Kraemer} %MDPI: Please carefully check the accuracy of names and affiliations. %Authors: we agree
 $^{1,}$*\orcidA{}, Frank Hellmann $^{1}$, Mehrnaz Anvari $^{1}$\orcidB{}, \hl{J\"urgen Kurths} %MDPI: The name of this author is different from the submitting system. Please confirm which one is correct. %Authors: we agree
 $^{1,2,\highlighting{3} %MDPI: 
}$ and Norbert Marwan $^{1,2,\highlighting{4} %MDPI: 
,}$*\orcidC{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Potsdam Institute for Climate Impact Research (PIK), Member of the Leibniz Association, 14473 Potsdam, Germany; \hl{hellmann@pik-potsdam.de (F.H.); anvari@pik-potsdam.de (M.A.); kurths@pik-potsdam.de (J.K.)} %MDPI: We added the email addresses here according to the submitting system. Please confirm.%Authors: we agree
\\
$^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
\hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes.%Authors: we agree
 \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany\\
\hl{$^{4}$} \quad Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany}

@@

Recurrence plots (RPs) provide a vivid representation of complex dynamics $\vec{x}_i$ stemming from potentially high dimensional systems \cite{marwan2007}
\begin{equation}\label{eq_rp_definition}
R_{i,j}(\varepsilon) = \Theta\left(\varepsilon - D_{i,j}\right) 
= \Theta\left(\varepsilon - \| \vec{x}_i - \vec{x}_j\|\right), \qquad \vec{x} \in \mathbb{R}^d, \quad i,j \in [1,\ldots, N],
\end{equation}
where $\mathbf{R}$ \hl{is} %MDPI: There is no bold in other places in the text, please confirm whether the bold here needs to be retained %Authors: we confirm that this is boldface, because it this variable represents a matrix
 the recurrence matrix, $\vec{x}_i$ is the state vector at time 
$t = \Delta t \cdot i$ ($\Delta t$ the sampling time), $N$ is the number of
sampling points (or length of data series), and $d$ is the dimension of the system.
The crucial free parameter $\varepsilon$ is the recurrence threshold, determining what is a recurrence
and, thus, the visible structures in the RP. It can be chosen such that the recurrence rate 
$RR(\varepsilon)=N^{-2}\sum_{i,j}^N R_{i,j}(\varepsilon)$ exhibits a certain value \cite{kraemer2018}.
The simple idea to track recurring states of the $d$-dimensional trajectory $\vec{x}_i$ of the system under study not only allows for a beneficial visualization of the dynamics, 
but also for its 
quantification, using certain structures in the RP, such as diagonal or vertical lines \cite{marwan2007}.
